Outputs from time slice analyses

### 2017-12-13 analyses/03-statistical-analyses.Rmd
Fixed NA bug in Bapst

## Test the effect of extinctions
mapply.test <- function(data, times, test = wilcox.test, correction = "bonferroni") {
  test <- try(output <- test.dispRity(data, test = test, comparisons = times, correction = correction), silent = TRUE)
  if(class(test) == "try-error") {

@@

>>>>

## Test the effect of extinctions
mapply.test <- function(data, times, test = wilcox.test, correction = "bonferroni") {
  test_run <- try(output <- test.dispRity(data, test = test, comparisons = times, correction = correction), silent = TRUE)
  if(class(test_run) == "try-error") {

    ## Try the test on less lags
    subsets_to_test <- unique(unlist(times))
    na_subsets <- summary(data)$obs[subsets_to_test]
    if(any(is.na(na_subsets))) {
      ## Remove the subsets with NA from the comparisons
      subsets_to_remove <- unlist(lapply(lapply(times, function(X) match(X, subsets_to_test[which(is.na(na_subsets))])), function(X) return(any(!is.na(X)))))

      ## Remove the subsets
      times_no_na <- times[!subsets_to_remove]
    } else {
      subsets_to_remove <- rep(TRUE, length(times))
    }

@@

    if(!all(subsets_to_remove)) {
      output <- test.dispRity(data, test = test, comparisons = times_no_na, correction = correction)

      ## Replacing the NAs
      statistic[!subsets_to_remove,1] <- output[[1]][,1]
      p_value[!subsets_to_remove,1] <- output[[2]][,1]
    }
